Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-24 cloneoverflow-latex/cloneoverflow.tex
Down to 10 pages of text!

\overfullrule1ex

@@

\textbf{Clone Detection Configuration: }
We were aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). The details of the two configurations are
described in \Cref{t:param_tuning}.

@@

@@

\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{good-ok_pairs}
	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
	\label{fig:good-ok-pairs}
\end{figure}

The distribution of \textit{good} clone pairs between the four
combinations of \textit{D} and \textit{E} configurations are listed in
\Cref{t_agreed_good_clone_pairs}.  There are 2,326 (2,313 unique)
\textit{good} pairs consisting of 23 pairs from $S_D$--$N_D$, 26 pairs
from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
$S_E$--$N_E$. There are 33,156 (32,316 unique) \textit{ok}
pairs\footnote{This excludes the subsumed 2,313 \textit{good}
  pairs. According to the definition, \textit{ok} pairs always subsume
  \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
respectively. Between the four configuration sets, there is
considerable amount of clone pairs shared between two adjacent sets
(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
that is agreed by all four combinations.

@@

Regarding the online cloning classification patterns, 
we studied the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. 
We have tried to classify 697 online clone pairs from
the reported clones in phase 1 
%Using the $S_D$ clone report,
%snippets were ranked according to (1)~clone pair frequency,
%(2)~popularity (i.e.~number of associated Qualitas projects),
%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
%selected these four criteria so that we could cover the online clones
%from various aspects. We selected the top 10 from each ranking and
%obtained 34 unique Stack Overflow snippets. The snippets were
%associated with 697 clone pairs.
%\subsubsection{Defining Online Code Cloning Patterns}
using Kapser's cloning patterns. We found that the
clone pairs were categorised into either Customisation or Templating.
Thus, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.
Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
containing boiler-plate code of {\small\verb|equals()|} methods,
getters/setters, or IDE-generated code such as GUI components. Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c@{~~}p{7.35cm}}
			\hline 
			Patt. & Description \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

@@

The number of online clone pairs reported by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

@@

During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 1,216 true positive clone pairs between 516 Stack
Overflow snippets and 75 Qualitas projects.

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
online clone pairs with evidences of cloning from Qualitas projects to
Stack Overflow. They include 3, 14, 86, and 9 pairs from the
\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
them have a statement in the Stack Overflow post saying that the code
is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
Qualitas project. For example, according to the motivating example in 
\Cref{fig:before-after}, we found evidence in the Stack Overflow 
Post 22315734 saying that \textit{``Actually, you can learn how to compare 
in Hadoop from WritableComparator. Here is an examle that borrows 
some ideas from it.''}

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
any clone pairs with evidence of cloning from Stack Overflow to
Qualitas projects.

\textbf{EX: External Sources.} We found 200 online clone pairs with
evidence of cloning from external sources to Stack Overflow. 
They include 4, 44, 146, and 6 clone pairs from the \textit{good},
\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
contain statements showing an external source of the cloned code.
For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
	changed only the hash algorithm.''}

These findings complement a study of clones between software
projects~\cite{Svajlenko2014}. We found that the code cloning can also
happen among different sources on the Internet just like software
projects. There are 30 clone pairs that originated from programming
websites. For example, we found a clone of code snippet to convert
numbers into words which is copied from
\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
Overflow and the \textsf{compiere} project source code contain an
attribution to the original source. Another example is a code snippet
to generate graphical \textit{Perlin noise}. It is copied from
\url{http://mrl.nyu.edu/~perlin/noise/}. The code is used on Stack
Overflow and in the \textsf{aoi} project with
attribution.
% The original code of the 15 clone pairs do not have licensing
% information so these clones do not violate any license.
There are other EX clone pairs which are copied from third-party
libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
project.

@@

\textbf{For RQ3, our results show that more than half (64) of QS clone
  pairs on Stack Overflow are outdated. 60 pairs differ from their
  newest versions by modifications applied to variable names or method
  names, added or deleted statements, to a fully rewritten code with
  new method signatures. 4 pairs are dead
  snippets.}

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	%\small
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
                  modified/added/deleted statements, \textit{D}: file
                  has been deleted,  \textit{R}: method has been
                  rewritten completely}}
		\end{tabular} %
	%}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{1.95cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
		& MIT-like & MIT-like & 0 & 1 & 0\\
		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
		& No license & No license & 5 & 4 & 21 \\
		\hline
		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
		& No license & Apache-2 & 41 & 6 & 23 \\
		& No license & BSD3 & 3 & 4 & 28 \\
		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
		& No license & CDDLv1 & 0 & 1 & 0 \\
		& No license & EPLv1 & 7 & 0 & 10 \\
		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
		& No license & MPLv1.1 & 0 & 0 & 1 \\
		& No license & spdxBSD3 & 0 & 0 & 10 \\
		& No license & SPLv1 & 0 & 1 & 0 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\textbf{Internal validity:}

We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two, instead of one, widely-used
clone detection tools, Simian and NiCad.  We had tried three other
clone detectors but could not add them to the study due to their
scalability issue and susceptibility to incomplete code snippets.
Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good} and
\textit{ok} criteria had a higher chance to be true positive. We also
applied the Bellon's clone agreement to 4 different combinations of
the tools' configurations.  For disagreed clone pairs, we applied
several filters to remove spurious and uninteresting clones.

The number of online clones we found are subject to the clone
detectors and their configurations.  We mitigated the problem of clone
detector's parameter sensitivity by adding another configuration,
besides the default configuration. We reused the established
configurations from the EvaClone study~\cite{Wang2013}.  We also
performed a pairwise matching between the default and EvaClone
configurations of the two clone detection tools.

@@

The 3,632 clone pairs classified manually by the first author are
subject to manual judgement and human errors.  Although we have tried
our best to be careful on searching for evidence and classifying the
clones, some errors may still exist. We mitigated this problem by
having the second author to validate the classifications with a random
sampling.  The 64 classification conflicts were discussed and
resolved.  The third author made a final judgement when no consensus
could be found by the two authors.
 %In addition, we are aware of voting mechanism
%in Stack Overflow and plan to incorporate highest-vote answers in the future work.

@@

Regarding the code snippets, we downloaded a full data dump and
extracted Java accepted answers. Instead of analysing every post, we
only focused on posts marked as accepted answers since they are the
most likely ones to be reused. This yields a total of 144,064
snippets.  Our findings are limited to these restrictions. They may
not be generalised to all programming languages and all answers on
Stack Overflow. On the other hand, we chose the curated Qualitas
corpus for Java open source projects containing 111 projects
\cite{QualitasCorpus}.  The projects span over several areas of
software and has been used in several empirical
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
it is a curated and well-established corpus, it may not fully
represent all Java open source software available.

@@

\textbf{Stack Overflow} is a gold mine for software engineering research. Its rich and developer-driven data are invaluable. Since posts on Stack Overflow may contain code snippets embedded within natural language text, they become a huge database for source code and code-relevant information. The Stack Overflow data set has been put to use in several previous studies. In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}. A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms. The code snippets on Stack Overflow are mostly examples or solutions to programming problems. Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.

Another research area is knowledge extraction from Stack Overflow. Nasehi et al.~\cite{Nasehi2012}~studied what makes a good code example by analysing answers from Stack Overflow. Similarly, Yang et al.~\cite{Yang2016} report the number of reusable code snippets on Stack Overflow across various programming languages. Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions. There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.

>>>>

%\overfullrule1ex

@@

\textbf{Clone Detection Configuration: }
We are aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.

@@

The number of online clone pairs reported % by running Simian and NiCad
are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
respectively. This is expected since EvaClone configurations prefer
recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
$N_D$ has an average clone size of 10.85 lines which is bigger than
6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
configuration with a smaller minimum size (\Cref{t:param_tuning}).

@@

\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold of 0.7 for
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{good-ok_pairs}
	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
	\label{fig:good-ok-pairs}
\end{figure}

The distribution of \textit{good} clone pairs between the four
combinations of \textit{D} and \textit{E} configurations are listed in
\Cref{t_agreed_good_clone_pairs}.  There are 2,326 (2,313 unique)
\textit{good} pairs consisting of 23 pairs from $S_D$--$N_D$, 26 pairs
from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
$S_E$--$N_E$. There are 33,156 (32,316 unique) \textit{ok}
pairs\footnote{This excludes the subsumed 2,313 \textit{good}
  pairs because \textit{ok} pairs subsume
  \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
respectively. Between the four configuration sets, there is
considerable amount of clone pairs shared between two adjacent sets
(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
that is agreed by all four combinations.

@@

Regarding the online cloning classification patterns, 
we studied the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. 
We tried to classify 697 online clone pairs from
the reported clones in phase 1 
%Using the $S_D$ clone report,
%snippets were ranked according to (1)~clone pair frequency,
%(2)~popularity (i.e.~number of associated Qualitas projects),
%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
%selected these four criteria so that we could cover the online clones
%from various aspects. We selected the top 10 from each ranking and
%obtained 34 unique Stack Overflow snippets. The snippets were
%associated with 697 clone pairs.
%\subsubsection{Defining Online Code Cloning Patterns}
using Kapser's cloning patterns. We found that 
% the
% clone pairs were categorised into either Customisation or Templating.
% Thus, 
Kapser's patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.
Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
containing boiler-plate code of {\small\verb|equals()|} methods,
getters/setters, or IDE-generated code such as GUI components. Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}\vspace{-1ex}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
        \small\vspace{-1ex}
		\begin{tabular}{c@{~~}p{7.35cm}}
			\hline 
			Patt. & Description \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

@@

@@

During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the set still contains 1,216 true positive clone pairs between 516 Stack
Overflow snippets and 75 Qualitas projects.

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
online clone pairs with evidences of cloning from Qualitas projects to
Stack Overflow. They include 3, 14, 86, and 9 pairs from the
\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
them have a statement in the Stack Overflow post saying that the code
is ``copied'', ``borrowed'' or ``modified'' from a specific file or class in a
Qualitas project. For example, according to the motivating example in 
\Cref{fig:before-after}, we found evidence in the Stack Overflow 
Post 22315734 saying that \textit{``Actually, you can learn how to compare 
in Hadoop from WritableComparator. Here is an examle that borrows 
some ideas from it.''}

@@

\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
any pairs with evidence of cloning from Stack Overflow to Qualitas
projects. This is very likely due to the age of the Qualitas corpus.

\textbf{EX: External Sources.} We found 200 online clone pairs with
evidence of cloning from external sources to Stack Overflow.  They
include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
$S_D'$, and $N_D'$ set respectively. All of them contain statements
giving an external source of the cloned code.  For example, Stack
Overflow Post 9549009 contains a code comment saying \textit{``Copied
  shamelessly from
  org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''}.

These findings complement a study of clones between software
projects~\cite{Svajlenko2014}. We found that cloning can also
happen among different sources on the Internet just like software
projects. There are 30 clone pairs that originated from programming
websites. For example, we found a clone of a snippet to convert
numbers into words which is copied from
\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
Overflow and the \textsf{compiere} project code contain an
attribution to the original source. Another example is a snippet
to generate graphical \textit{Perlin noise}. It is copied from
\url{http://mrl.nyu.edu/~perlin/noise/} and is used on Stack
Overflow and in the \textsf{aoi} project with
attribution.
% The original code of the 15 clone pairs do not have licensing
% information so these clones do not violate any license.
There are other EX pairs which are copied from third-party
libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
project.

@@

\textbf{For RQ3, our results show that more than half (64) of QS clone
  pairs on Stack Overflow are outdated. 60 pairs differ from their
  newest versions by modifications applied to variable names or method
  names, added or deleted statements, to a fully rewritten code with
  new method signatures. 4~pairs are dead
  snippets.}

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	\small
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
                  modified/added/deleted statements, \textit{D}: file
                  has been deleted,  \textit{R}: method has been
                  rewritten completely}}
		\end{tabular} %
	%}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	\footnotesize
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{1.95cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
		& MIT-like & MIT-like & 0 & 1 & 0\\
		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
		& No license & No license & 5 & 4 & 21 \\
		\hline
		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
		& No license & Apache-2 & 41 & 6 & 23 \\
		& No license & BSD3 & 3 & 4 & 28 \\
		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
		& No license & CDDLv1 & 0 & 1 & 0 \\
		& No license & EPLv1 & 7 & 0 & 10 \\
		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
		& No license & MPLv1.1 & 0 & 0 & 1 \\
		& No license & spdxBSD3 & 0 & 0 & 10 \\
		& No license & SPLv1 & 0 & 1 & 0 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\textbf{Internal validity:} 
%
We could not verify all the 315,786,118 clone pairs reported by the
clone detection tools in this study.  Nevertheless, we applied
different mechanisms to ensure the validity to the subset of clone
pairs we classified.  First, we used two widely-used
clone detection tools, Simian and NiCad.  We tried three other
clone detectors but could not add them to the study due to their
scalability issues and susceptibility to incomplete code snippets.
Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
to prioritise and filters clone pairs for the manual
classification. The agreed clone pairs that passed \textit{good} and
\textit{ok} criteria had a higher chance to be true positive. 
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

% The number of online clones we found are subject to the clone
% detectors and their configurations.  
We mitigated the problem of clone
detector's parameter sensitivity by adding another established
configuration from the EvaClone study~\cite{Wang2013}.

% We also
% performed a pairwise matching between the default and EvaClone
% configurations of the two clone detection tools.

@@

The 3,632 clone pairs classified manually by the first author are
subject to manual judgement and human errors.  Although we have tried
our best to be careful on searching for evidence and classifying the
clones, some errors may still exist. We mitigated this problem by
having the second author to validate the classifications with a random
sampling. 
% The 64 classification conflicts were discussed and
% resolved.  
The third author made a final judgement when no consensus
could be found by the two authors.
 %In addition, we are aware of voting mechanism
%in Stack Overflow and plan to incorporate highest-vote answers in the future work.

@@

Regarding the code snippets, we downloaded a full data dump and
extracted Java accepted answers
% Instead of analysing every post, we
only focused on posts marked as accepted answers 
since they are the
most likely ones to be reused. 
% This yields a total of 144,064 snippets.  
Our findings are limited to these restrictions. They may
not be generalised to all programming languages and all answers on
Stack Overflow. We chose the curated Qualitas
corpus for Java open source projects containing 111 projects
\cite{QualitasCorpus}.  The projects span over several areas of
software and has been used in several empirical
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
it is a curated and well-established corpus, it may not fully
represent all Java open source software available.

@@

\textbf{Stack Overflow} is a gold mine for software engineering
research and
% Its rich and developer-driven data are invaluable. Since
% posts on Stack Overflow may contain code snippets embedded within
% natural language text, they become a huge database for source code and
% code-relevant information. 
%The Stack Overflow data set 
has been put to
use in several previous studies. In terms of developer-assisting
tools, Seahawk is an Eclipse plug-in that searches and recommends
relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}. A
follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014}
achieves the same goal but with improved algorithms. The code snippets
on Stack Overflow are mostly examples or solutions to programming
problems. Hence, several code search systems use whole or partial data
from Stack Overflow as their code search
databases~\cite{Keivanloo2014,Park2014,
  Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude
et al.~\cite{Treude2016}~use machine learning techniques to extract
insight sentences from Stack Overflow and use them to improve API
documentation.

Another research area is knowledge extraction from Stack
Overflow. Nasehi et al.~\cite{Nasehi2012}~studied what makes a good
code example by analysing answers from Stack Overflow. Similarly, Yang
et al.~\cite{Yang2016} report the number of reusable code snippets on
Stack Overflow across various programming languages. Wang et
al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation
(LDA) topic modelling to analyse questions and answers from Stack
Overflow so that they can automatically categorise new
questions. There are also studies trying to understand developers'
behaviours on Stack Overflow,
e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
% , while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.

\textbf{Code clone detection} is a long-standing research topic in
software engineering. Whether clones are good or bad for software is
still
controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
% However, by only knowing how many code clones residing in software
% and how they evolve~\cite{Pate2013,Mondal2011} can provide several
% valuable insights into the software systems.
Code clones have several
applications such as software plagiarism
detection~\cite{Prechelt2002}, source code
provenance~\cite{Davies2013}, and software licensing
conflicts~\cite{German2009}.
